Subject-level developmental relationships

### 2024-09-27 3_developmental_relationships.qmd
up to date for call

```{r, fig.width=9, fig.height=9}
GGally::ggpairs(select(d_sub, age, log_age, rt, log_rt, 
                       short_window_accuracy, long_window_accuracy, 
                       short_window_elogit, long_window_elogit, prod, comp), 
                progress = FALSE, lower = list(continuous = GGally::wrap("points", alpha = 0.03)))

@@

fa.parallel(d_sub_mat)
```
```{r}
mod1 <- fa(d_sub_mat, 1, rotate = "varimax")

@@

summary(fit)
a <- graph_sem(model = fit)+ theme(panel.background = element_rect(fill = "white"))
```

@@

summary(fit_prod)
b <- graph_sem(model = fit_prod) + 
  theme(panel.background = element_rect(fill = "white"))
b
```
```{r}
d_cfa_comp <- d_sub |>
             rename(`accuracy` = long_window_accuracy) |>
             mutate(accuracy = scale(accuracy), 
                    log_age = scale(log_age), 
                    log_rt = scale(log_rt), 
                    comp = scale(comp)) |>
  select(accuracy, log_age, log_rt, comp)

@@

@@

@@

@@

The next thing to do is look at any longitudinal data we have, to see how predictive faster LWL at t0 is of higher CDIs at t1.

>>>>

```{r}
GGally::ggpairs(select(d_sub, age, log_age, rt, log_rt, 
                       short_window_accuracy, long_window_accuracy, 
                       short_window_elogit, long_window_elogit, prod, comp), 
                progress = FALSE, lower = list(continuous = GGally::wrap("points", alpha = 0.03)))

@@

```{r}
mod1 <- fa(d_sub_mat, 1, rotate = "varimax")
mod1

@@

summary(fit)
a <- graph_sem(model = fit)+ theme(panel.background = element_rect(fill = "white"))
```
Production.

@@

summary(fit_prod)
b <- graph_sem(model = fit_prod) + 
  theme(panel.background = element_rect(fill = "white"))
b
```

Comprehension.

```{r}
d_cfa_comp <- d_sub |>
             rename(`accuracy` = long_window_accuracy) |>
             mutate(accuracy = scale(accuracy), 
                    log_age = scale(log_age), 
                    log_rt = scale(log_rt), 
                    comp = scale(comp)) |>
  select(accuracy, log_age, log_rt, comp)

@@

Plot these as a grid.

@@

## Measurement invariance across age?

```{r}
fa_model <-  "F1  =~ log_age + log_rt + accuracy"
fit_younger <- cfa(fa_model, 
                   filter(d_cfa, log_age <= median(log_age)),
                   std.lv=TRUE)

graph_sem(model = fit_younger)
```

@@

## Without CDIs

```{r}
ggplot(d_sub_long, 
       aes(x = age, y = long_window_accuracy, group = subject_id, col = dataset_name)) +
  geom_line(alpha = .3, position = position_jitter(width = .1, height = 0)) + 
  geom_smooth(aes(group = 1)) + 
  scale_y_log10() + 
  geom_hline(lty = 2, yintercept = .5)

```{r}
ggplot(filter(d_sub_long, n_trials_rt > 3),
       aes(x = age, y = log_rt, group = subject_id, col = dataset_name)) +
  geom_line(alpha = .3, position = position_jitter(width = .1, height = 0)) + 
  geom_smooth(aes(group = 1)) + 
  scale_y_log10() 
```

## Model comparison of growth forms within kids

@@
